---
title: "Assignment 1"
author: "Sezer Turkmen"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 1
editor: visual
---

# \| ABOUT ME

<span style="font-size: 20px;">Greetings!</span> 

I'm **Sezer Turkmen**, a software developer whose journey spans the realms of architecture and coding. In a nutshell:

### From Architect to Code Creator: My Transition

I initially ventured into the world of architecture, my first passion. My studies took me to Italy, where I delved into multi-scale architecture and sustainable design, honing my eye for detail and love for harmonious structures.

After working as an architect for a considerable period, I felt the magnetic pull towards coding. The allure of shaping digital landscapes was irresistible, prompting a career shift.

### Mastering Full Stack Development

As a software developer, I immersed myself in coding, mastering Java and venturing into full-stack development. I used technologies like Spring Boot and React to craft dynamic, user-friendly applications. Kubernetes and Docker added efficiency and scalability to my toolkit, bridging the worlds of traditional and digital architecture.

My journey is guided by the belief in perpetual learning. I attended a coding bootcamp to refine my skills and gain practical insights, cementing my passion for coding. As a software developer, I enjoy creating elegant, user-centric applications.

Currently, I'm pursuing a master's in Information Technologies at MEF University, ensuring my knowledge stays cutting-edge.

### Life Beyond Tech

Outside of coding and architecture, I find joy in cooking, a creative outlet where flavors and textures are my canvas. Staying active is another passion. Whether it's hitting the gym or enjoying indoor cycling with a spirited playlist, I cherish the rhythm and precision of physical activity.

### The Future Awaits

I'm Sezer Turkmen, a full-stack developer, architect, and a lover of life. My mission is to blend creativity and technology, one line of code at a time. Thank you for getting to know me!

[![LinkedIn Badge](https://img.shields.io/badge/linkedin-%230077B5.svg?&style=for-the-badge&logo=linkedin&logoColor=white&color=071A2C)](https://www.linkedin.com/in/sezerlucianturkmen/) [![Medium Badge](https://img.shields.io/badge/medium-%2312100E.svg?&style=for-the-badge&logo=medium&logoColor=white&color=071A2C)](https://medium.com/@sezerlucianturkmen) [![Instagram Badge](https://img.shields.io/badge/instagram-%23E4405F.svg?&style=for-the-badge&logo=instagram&logoColor=white&color=071A2C)](https://www.instagram.com/sezer.who/)

# \| GO POSIT

### YouTube Channel \| The open-source data science company for the individual, team and enterprise.

<div style="text-align: center;">
  <iframe width="560" height="315" src="https://www.youtube.com/embed/Fja5DIN3uTw" frameborder="0" allowfullscreen style="display: inline-block;"></iframe>
</div>


[*Teaching R online with RStudio Cloud*](https://www.youtube.com/watch?v=Fja5DIN3uTw&list=PL9HYL-VRX0oTOK4cpbCbRk15K2roEgzVW&index=127)

I chose to watch the video titled **"Mine Çetinkaya-Rundel \| Teaching R online with RStudio Cloud"** for two main reasons. Firstly, I was interested in learning about effective online teaching methods for the R programming language, commonly used in data science. The video delves into the benefits of using RStudio Cloud for teaching, emphasizing its user-friendly approach. Additionally, I was drawn to the fact that the presenter, Mine Çetinkaya-Rundel, shares a Turkish background with me, which added a unique cultural perspective to the subject matter. The presentation covers tips and best practices for using RStudio Cloud effectively in the classroom, as exporting and grading student work and sharing data files.

# \| SEE DATASET

```{r data , include=FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyverse)


```

# \| LEARN THREE R POST

This is a template example qmd output page. You may see an example R code below.

```{r}
set.seed(1)
vec1 <- sample(LETTERS,5)
paste0(vec1,collapse="")
```
