---
title: "Assignment 1"
author: "Sezer Turkmen"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 1
    number_sections: true
editor: visual
---

# \| ABOUT ME

[Greetings!]{style="font-size: 20px;"}

I'm **Sezer Turkmen**, a software developer whose journey spans the realms of architecture and coding. In a nutshell:

### From Architect to Code Creator: My Transition

I initially ventured into the world of architecture, my first passion. My studies took me to Italy, where I delved into multi-scale architecture and sustainable design, honing my eye for detail and love for harmonious structures.

After working as an architect for a considerable period, I felt the magnetic pull towards coding. The allure of shaping digital landscapes was irresistible, prompting a career shift.

### Mastering Full Stack Development

As a software developer, I immersed myself in coding, mastering Java and venturing into full-stack development. I used technologies like Spring Boot and React to craft dynamic, user-friendly applications. Kubernetes and Docker added efficiency and scalability to my toolkit, bridging the worlds of traditional and digital architecture.

My journey is guided by the belief in perpetual learning. I attended a coding bootcamp to refine my skills and gain practical insights, cementing my passion for coding. As a software developer, I enjoy creating elegant, user-centric applications.

Currently, I'm pursuing a master's in Information Technologies at MEF University, ensuring my knowledge stays cutting-edge.

### Life Beyond Tech

Outside of coding and architecture, I find joy in cooking, a creative outlet where flavors and textures are my canvas. Staying active is another passion. Whether it's hitting the gym or enjoying indoor cycling with a spirited playlist, I cherish the rhythm and precision of physical activity.

### The Future Awaits

I'm Sezer Turkmen, a full-stack developer, architect, and a lover of life. My mission is to blend creativity and technology, one line of code at a time. Thank you for getting to know me!

[![LinkedIn Badge](https://img.shields.io/badge/linkedin-%230077B5.svg?&style=for-the-badge&logo=linkedin&logoColor=white&color=071A2C)](https://www.linkedin.com/in/sezerlucianturkmen/) [![Medium Badge](https://img.shields.io/badge/medium-%2312100E.svg?&style=for-the-badge&logo=medium&logoColor=white&color=071A2C)](https://medium.com/@sezerlucianturkmen) [![Instagram Badge](https://img.shields.io/badge/instagram-%23E4405F.svg?&style=for-the-badge&logo=instagram&logoColor=white&color=071A2C)](https://www.instagram.com/sezer.who/)

---

# \| DISCOVER THE POSIT

### YouTube Channel \| The open-source data science company for the individual, team and enterprise.

::: {style="text-align: center;"}
<iframe width="560" height="315" src="https://www.youtube.com/embed/Fja5DIN3uTw" frameborder="0" allowfullscreen style="display: inline-block;"></iframe>
:::

[*Teaching R online with RStudio Cloud*](https://www.youtube.com/watch?v=Fja5DIN3uTw&list=PL9HYL-VRX0oTOK4cpbCbRk15K2roEgzVW&index=127)

I chose to watch the video titled **"Mine Çetinkaya-Rundel \| Teaching R online with RStudio Cloud"** for two main reasons. Firstly, I was interested in learning about effective online teaching methods for the R programming language, commonly used in data science. The video delves into the benefits of using RStudio Cloud for teaching, emphasizing its user-friendly approach. Additionally, I was drawn to the fact that the presenter, Mine Çetinkaya-Rundel, shares a Turkish background with me, which added a unique cultural perspective to the subject matter. The presentation covers tips and best practices for using RStudio Cloud effectively in the classroom, as exporting and grading student work and sharing data files.

---

# \| PROPOSE DATASET

### Most Streamed Spotify Songs 2023


The 'Most Streamed Spotify Songs 2023' dataset is a fantastic choice for class demos. It offers insights into the music industry by showcasing popular songs and their attributes. Students can explore the science of hit songs, understand their impact through social media analysis, and learn about cross-platform music data. It's engaging and up-to-date, making it an excellent teaching resource.



```{r include=FALSE}

library(tidyverse)
library(googledrive)
library(dplyr)
library(readr)
library(ggplot2)
library(DT)


id <- "1nM0Cr-gVFF9UjvxSZXHNfFnrDWIUoTHi"
total_list <- read.csv(sprintf("https://docs.google.com/uc?id=%s&export=download", id))



 
```
```{r most_streamed_spotify_song_2023, include=TRUE}

# Filter out rows with non-numeric values in the 'streams' column
filtered_spotify_data <- total_list %>%
   filter(!grepl("[a-zA-Z]", streams))

# Sort the filtered dataset by the 'streams' column in descending order
sorted_filtered_spotify_data <- filtered_spotify_data %>%
  arrange(desc(streams))

# Create HTML view of Dataset
DT::datatable(head(sorted_filtered_spotify_data), editable = list(
  target = 'row', disable = list(columns = c(1, 3, 4))
))
 
```
---

*The* **Most Streamed Spotify Songs 2023** *dataset contains a comprehensive list of the most famous songs of 2023 as listed on Spotify. The dataset offers a wealth of features beyond what is typically available in similar datasets. It provides insights into each song's attributes, popularity, and presence on various music platforms. The dataset includes information such as track name, artist(s) name, release date, Spotify playlists and charts, streaming statistics, Apple Music presence, Deezer presence, Shazam charts, and various audio features.*

---

# \| LEARN THREE R POST

This is a template example qmd output page. You may see an example R code below.

```{r }
set.seed(1)
vec1 <- sample(LETTERS,5)
paste0(vec1,collapse="")
```
